Low load operating protocol investigation of a 620MWe power boiler using a fast Eulerian-Eulerian CFD model

### 2021-08-30 PAPER_2/PAPER_2_REV1.tex
Update - 30/08/2021

\documentclass[review]{elsarticle}
\usepackage[utf8]{inputenc} 
\usepackage{lineno,hyperref}
\modulolinenumbers[5]

@@

\title{Low load investigation of a 620MWe power boiler using fast Eulerian-Eulerian CFD model}

@@

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

@@

\begin{center}
\begin{tabular}{ |llllll| } 
 \hline
\multicolumn{3}{|c}{\textbf{Nomenclature}} & & &\\
& & & & & \\
\textit{Symbol} & \textit{Quantity} & \textit{Unit} & & &\\
A &  Area & $m^2$ & g & Gravity & $m/s^2$\\
 \hline
\end{tabular}
\end{center}

@@

\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

@@

\subsection{Model validation}

>>>>

\documentclass[review]{elsarticle}
\usepackage[utf8]{inputenc} 
\usepackage{lineno,hyperref}
\usepackage{tabu}
\usepackage{tabularx}
\usepackage{subfigure}
\modulolinenumbers[5]

@@

\title{Low load operating protocol investigation of a 620MWe power boiler using a fast Eulerian-Eulerian CFD model}

@@

\begin{abstract}

This template helps you to create a properly formatted \LaTeX\ manuscript.
Low load operation of utility boiler

\end{abstract}

@@

\begin{center}
\begin{tabular}{|p{0.1\textwidth}p{0.25\textwidth}p{0.05\textwidth}p{0.1\textwidth}p{0.25\textwidth}p{0.05\textwidth}|} 
 \hline
\multicolumn{3}{|c}{\textbf{Nomenclature}} & &  &\\
& & & & & \\
& &  & \multicolumn{3}{l|}{\textit{Greek letters}}\\
\textit{Symbol} & \textit{Quantity} & \textit{Unit} & $\alpha_p$ & Particle absorption coefficient &$m^{-1}$\\
A &  Area & $m^2$ & g & Gravity  & $m/s^2$\\
 \hline
\end{tabular}
\end{center}

@@

If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

@@

\begin{table}[h!]
\centering
\caption{Utility boiler fuel characteristics}
\vspace{5mm}
\label{fuel}
{\tabulinesep=1.2mm
\begin{tabularx}{\textwidth}{p{0.45\textwidth} p{0.3\textwidth} l}
\hline
\textbf{Fuel constituent} & \textbf{Fraction} & \textbf{Unit}\\
\hline
\textit{Ultimate analysis - (DAF)} & \textit{-} & \textit{-}\\
Carbon & $0.7753$ & $kg/kg_{fuel}$\\
Hydrogen & $0.0415$ & $kg/kg_{fuel}$\\
Nitrogen & $0.0181$ & $kg/kg_{fuel}$\\
Oxygen & $0.1474$ & $kg/kg_{fuel}$\\
Sulphur & $0.0175$ & $kg/kg_{fuel}$\\
\textit{Proximate analysis - (AR)} & \textit{-} & \textit{-}\\
Fixed carbon & $0.340$ & $kg/kg_{fuel}$\\
Volatile matter & $0.196$ & $kg/kg_{fuel}$\\
Ash & $0.4090$ & $kg/kg_{fuel}$\\
Moisture & $0.0550$ & $kg/kg_{fuel}$\\
\hline
\textbf{Energy content - (DAF)} & \textbf{Value} &\\
\hline
Higher heating value & $15070$ & $kJ/kg_{fuel}$\\
\hline
\end{tabularx}}
\end{table}

Validation separately mention the rates/loadings - give results for 40\% case inputs
Low Ultra low load inputs

\subsection{Model validation}
The validation of the proposed model was conducted for three steady state MCR loads of 100\%, 80\% and 60\%. The  
\\
Figures of the Histrograms and CO graphs as in paper
Data plots and overall performance of the model
Inputs for the various loads table

\begin{figure}\label{fig_heat_valid}
	\subfigure[]{\includegraphics[width=0.32\textwidth]{100_VALID_BAR}}
	\subfigure[]{\includegraphics[width=0.32\textwidth]{80_VALID_BAR}}
	\subfigure[]{\includegraphics[width=0.32\textwidth]{60_VALID_BAR}}
\caption{Validation of the experimental and models heat load to the furnace, PSH and HTSH for steady state loads of a) 100\% MCR, b) 80\% MCR and c) 60\% MCR}
\end{figure}

\begin{figure}\label{fig_comb_valid}
\centering
\subfigure[]{\includegraphics[width = 0.45\textwidth]{COPPM_VALID}}
\subfigure[]{\includegraphics[width = 0.45\textwidth]{XO2_VALID}}
\caption{Experimentally calculated $CO$ and $O_2$ concentration predictions at a height of 37.5 (m)}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale = 0.5]{TEMP_KEY}\\
\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_TEMP}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_TEMP}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_TEMP}}\\
\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_TEMP}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_TEMP}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_TEMP}}
\caption{Hi}
\end{figure}

ghff
\begin{figure}[h!]
\centering
\includegraphics[scale = 0.5]{VEL_KEY}\\
\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_VEL}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_VEL}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_VEL}}\\
\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_VEL}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_VEL}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_VEL}}
\caption{bye}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale = 0.5]{HEATFLUX_KEY}\\
\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT_HEATFLUX}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{MID_HEATFLUX}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM_HEATFLUX}}\\
\subfigure[]{\includegraphics[width=0.32\textwidth]{BOT05_HEATFLUX}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{MID05_HEATFLUX}}
\subfigure[]{\includegraphics[width=0.32\textwidth]{FBRM05_HEATFLUX}}
\caption{bye}
\end{figure}
